---
title: "Peroduce Plots"
author: "Pete Cuppernull"
date: "6/5/2021"
output: pdf_document
---

## Load packages
```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(zoo)
library(viridis)
```

## Load data
```{r}
data <- read_csv("data/embeddings-2d-d2v-all-subreddits.csv")
data_umap <- read_csv("data/embeddings-50d-umap-all-subreddits.csv")
```

## Prep Data for plots
```{r}
data <- data %>%
  select(Quarter, Year, label, Prompt, D2V_x, D2V_y) %>%
  mutate(Quarter = paste(0, Quarter, sep = "")) %>%
  mutate(date = paste(Quarter, Year, sep = "-")) %>%
  mutate(date = as.Date(as.yearqtr(date, "%q-%Y")))

```

## Plots - 2d embedding
```{r}
prompts <- data %>%
  select(Prompt) %>%
  distinct() %>%
  as.list()
```

Discrete Quarter Column
```{r}
data <- data %>%
  mutate(quarter_discrete = paste("Q", 
                                  substring(Quarter, 2),
                                  " ",
                                  as.character(Year),
                                  sep = "")) %>%
  mutate(quarter_discrete = factor(quarter_discrete,levels=c("Q1 2017",
                                                             "Q2 2017",
                                                             "Q3 2017",
                                                             "Q4 2017",
                                                             "Q1 2018",
                                                             "Q2 2018",
                                                             "Q3 2018",
                                                             "Q4 2018",
                                                             "Q1 2019",
                                                             "Q2 2019"))) %>%
  mutate(label = factor(label, levels = c("democrats", "conservative", "socialism"))) %>%
  select(-Quarter) %>%
  rename(Quarter = quarter_discrete)
  
```


### Scatter Plot of All Obs

By Quarter
```{r}
data %>%
    filter(Prompt == as.character(prompts$Prompt[2])) %>%
    mutate(Date = date) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(D2V_x, D2V_y, color = Date)) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompts$Prompt[2], "...\"", sep = ""),
         caption = "Trained on monthly r/Conservative corpus") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ label)
```

By Quarter
```{r}
data %>%
    #select(-Quarter) %>%
    filter(Prompt == as.character(prompts$Prompt[2])) %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(D2V_x, D2V_y, color = Subreddit), size = 1) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompts$Prompt[2], "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Quarter)
```


Function - wrap labels
```{r}
create_plot <- function(prompt){
  plot <- data %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(D2V_x, D2V_y, color = Date)) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Subreddit)
  
  ggsave(paste("plots/all-subreddits/main-scatter-subreddit-panel/", prompt, ".jpg", sep = ""),
         plot = plot,
         height = 4,
         width = 10)
}

```


```{r}
map(prompts$Prompt, create_plot)
```

Wrap Date
```{r}
create_plot_date <- function(prompt){
  plot <- data %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(D2V_x, D2V_y, color = Subreddit), size = 1) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Quarter)
  
  plot
  
  ggsave(paste("plots/all-subreddits/main-scatter-date-panel/", prompt, ".jpg", sep = ""), 
         plot = plot,
         height = 6,
         width = 10)  
}
```

```{r}
map(prompts$Prompt, create_plot_date)
```


Wrap Date == REMOVE CONSERVATIVE
```{r}
create_plot_date_NoCon <- function(prompt){
  plot <- data %>%
    filter(Prompt == as.character(prompt),
           label != "conservative") %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(D2V_x, D2V_y, color = Subreddit), size = 1) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Quarter)
  
  plot
  
  ggsave(paste("plots/all-subreddits/main-scatter-date-panel-NoCon/", prompt, ".jpg", sep = ""), 
         plot = plot,
         height = 6,
         width = 10)  
}
```

```{r}
map(prompts$Prompt, create_plot_date_NoCon)
```


### Scatter plot for D and S for Q2 2018 - all prompts panels
```{r}
plot <- data %>%
    filter(Quarter == "Q2 2018",
           label != "conservative") %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(D2V_x, D2V_y, color = Subreddit), size = 1) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "Embedding Results for Q2 2018",
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, 
             base_family='Times New Roman') +
    facet_wrap(~ Prompt,
               labeller = label_wrap_gen(width=30)) +
    theme(strip.text = element_text(size=10))
  
  ggsave("plots/all-subreddits/main-scatter-date-panel-NoCon/q2-2018.jpg",
         plot = plot,
         height = 6,
         width = 8)  

```




### Scatter Plot of Monthly Averages - wrap label
```{r}
create_plot_monthly_average <- function(prompt){
  plot <- data %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    group_by(Date, Subreddit) %>%
    summarize(x_avg = mean(D2V_x),
              y_avg = mean(D2V_y)) %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(x_avg, y_avg, color = Date)) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Subreddit)
  
  ggsave(paste("plots/all-subreddits/monthly-average-subreddit/", prompt, ".jpg", sep = ""), plot = plot)
}
```

```{r}
map(prompts$Prompt, create_plot_monthly_average)
```



```{r}
data %>%
    filter(Prompt == as.character(prompts$Prompt[2])) %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    group_by(Date, Subreddit) %>%
    summarize(x_avg = mean(D2V_x),
              y_avg = mean(D2V_y)) %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(x_avg, y_avg, shape = Subreddit, color = Date), size = 3) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompts$Prompt[2], "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman')
```

```{r}
create_plot_monthly_average_date <- function(prompt){
  plot <- data %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    group_by(Date, Subreddit) %>%
    summarize(x_avg = mean(D2V_x),
              y_avg = mean(D2V_y)) %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(x_avg, y_avg, color = Subreddit)) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Date)
  
  plot
   # ggsave(paste("plots/average-scatter/", prompt, ".jpg", sep = ""), plot = plot)
}
```

```{r}
map(prompts$Prompt, create_plot_monthly_average_date)
```



### Line Plot of Time and First Dimension
```{r}
line_plot_monthly_average <- function(prompt) {
plot <- data %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Date = date) %>%
    distinct() %>%
    group_by(Date) %>%
    summarize(x_avg = mean(D2V_x),
           y_avg = mean(D2V_y)) %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_line(aes(Date, x_avg)) +
    labs(x = "Month",
         y = "X Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly r/Conservative corpus") +
    theme_bw(base_size=12, base_family='Times New Roman') 

  ggsave(paste("plots/monthly-line-x/", prompt, ".jpg", sep = ""), plot = plot)
}
```

```{r}
map(prompts$Prompt, line_plot_monthly_average)
```

### Line Plot of Time and Second Dimension

```{r}
line_plot_monthly_average <- function(prompt) {
plot <- data %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Date = date) %>%
    distinct() %>%
    group_by(Date) %>%
    summarize(x_avg = mean(D2V_x),
           y_avg = mean(D2V_y)) %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_line(aes(Date, y_avg)) +
    labs(x = "Month",
         y = "X Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly r/Conservative corpus") +
    theme_bw(base_size=12, base_family='Times New Roman') 

  ggsave(paste("plots/monthly-line-y/", prompt, ".jpg", sep = ""), plot = plot)
}
```

```{r}
map(prompts$Prompt, line_plot_monthly_average)
```

### Test threshold before/after cambridge analytica

Basically, repeat the main scatter plot above but for February and April 2018.

Filter data
```{r}
data_c <- data %>%
  filter(date == "2018-02-01" | date == "2018-04-01")
```

```{r}
data_prompts <- read_csv("data/embeddings-2d-d2v.csv")
```

```{r}
data_prompts %>%
  select(Month, Year, Prompt, Result) %>%
  filter((Month == 2 & Year == 2018 & Prompt == "Facebook's impact on democracy is") |
           (Month == 4 & Year == 2018 & Prompt == "Facebook's impact on democracy is"))
```


```{r}
create_plot <- function(prompt){
  plot <- data_c %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Month = if_else(Month == "02", "February 2018", "April 2018")) %>%
    mutate(Date = date) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(D2V_x, D2V_y, color = Month)) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly r/Conservative corpus") +
    theme_bw(base_size=12, base_family='Times New Roman') 
  
  ggsave(paste("plots/spring-2018-scatter/", prompt, ".jpg", sep = ""), plot = plot)
  plot
}
```

```{r}
map(prompts$Prompt, create_plot)
```



## Plots - 50d embedding
```{r}
prompts <- data_umap %>%
  select(Prompt) %>%
  distinct() %>%
  as.list()
```

Discrete Quarter Column
```{r}
data_umap <- data_umap %>%
  mutate(quarter_discrete = paste("Q", 
                                  as.character(Quarter),
                                  " ",
                                  as.character(Year),
                                  sep = "")) %>%
  mutate(quarter_discrete = factor(quarter_discrete,levels=c("Q1 2017",
                                                             "Q2 2017",
                                                             "Q3 2017",
                                                             "Q4 2017",
                                                             "Q1 2018",
                                                             "Q2 2018",
                                                             "Q3 2018",
                                                             "Q4 2018",
                                                             "Q1 2019",
                                                             "Q2 2019"))) %>%
  mutate(label = factor(label, levels = c("democrats", "conservative", "socialism"))) %>%
  select(-Quarter) %>%
  rename(Quarter = quarter_discrete)
  
```


### Scatter Plot of All Obs

By Quarter
```{r}
data_umap %>%
    filter(Prompt == as.character(prompts$Prompt[2])) %>%
    mutate(Date = date) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(D2V_x, D2V_y, color = Date)) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompts$Prompt[2], "...\"", sep = ""),
         caption = "Trained on monthly r/Conservative corpus") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ label)
```

By Quarter
```{r}
data_umap %>%
    #select(-Quarter) %>%
    filter(Prompt == as.character(prompts$Prompt[5])) %>%
    mutate(Subreddit = label) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(umap_x, umap_y, color = Subreddit), size = 1) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "UMAP Projects of 50-D D2V Text Generation Results",
         subtitle = paste("Prompt: \"", prompts$Prompt[2], "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Quarter)
```


Function - wrap labels

```{r}
data_umap %>%
    filter(Prompt == as.character(prompts$Prompt[5])) %>%
    mutate(Subreddit = label) %>%
    mutate(Quarter = as.Date(as.yearqtr(Quarter, "Q%q %Y"))) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(umap_x, umap_y, color = Quarter), size = .5) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "UMAP Projections of 50-Dimensional Doc2Vec Results",
         subtitle = paste("Prompt: \"", prompts$Prompt[5], "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Subreddit)

```

```{r}
create_plot <- function(prompt){
  plot <- data_umap %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Subreddit = label) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(umap_x, umap_y, color = Quarter)) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "UMAP Projections of 50-Dimensional Doc2Vec Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Subreddit)
  
  ggsave(paste("plots/umap/main-scatter-subreddit-panel/", prompt, ".jpg", sep = ""),
         plot = plot,
         height = 4,
         width = 10)
}

```


```{r}
map(prompts$Prompt, create_plot)
```

Wrap Date
```{r}
create_plot_date <- function(prompt){
  plot <- data_umap %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Subreddit = label) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(umap_x, umap_y, color = Subreddit), size = 1) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "UMAP Projections of 50-Dimensional Doc2Vec Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Quarter)
  
  plot
  
  ggsave(paste("plots/umap/main-scatter-date-panel/", prompt, ".jpg", sep = ""), 
         plot = plot,
         height = 6,
         width = 10)  
}
```

```{r}
map(prompts$Prompt, create_plot_date)
```


Wrap Date == REMOVE CONSERVATIVE
```{r}
create_plot_date_NoCon <- function(prompt){
  plot <- data_umap %>%
    filter(Prompt == as.character(prompt),
           label != "conservative") %>%
    mutate(Subreddit = label) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(umap_x, umap_y, color = Subreddit), size = 1) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "UMAP Projections of 50-Dimensional Doc2Vec Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Quarter)
  
  plot
  
  ggsave(paste("plots/umap/main-scatter-date-panel-NoCon/", prompt, ".jpg", sep = ""), 
         plot = plot,
         height = 6,
         width = 10)  
}
```

```{r}
map(prompts$Prompt, create_plot_date_NoCon)
```


### Scatter plot for D and S for Q2 2018 - all prompts panels
```{r}
plot <- data %>%
    filter(Quarter == "Q2 2018",
           label != "conservative") %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(D2V_x, D2V_y, color = Subreddit), size = 1) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "Embedding Results for Q2 2018",
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, 
             base_family='Times New Roman') +
    facet_wrap(~ Prompt,
               labeller = label_wrap_gen(width=30)) +
    theme(strip.text = element_text(size=10))
  
  ggsave("plots/all-subreddits/main-scatter-date-panel-NoCon/q2-2018.jpg",
         plot = plot,
         height = 6,
         width = 8)  

```


#### Scatter pplot H1 2018 for eahc subreddit

```{r}
plot <- data_umap %>%
    filter(Prompt == as.character(prompts$Prompt[5]),
           Quarter == "Q1 2018" | Quarter == "Q2 2018") %>%
    mutate(Subreddit = label) %>%
  #  mutate(Quarter = as.Date(as.yearqtr(Quarter, "Q%q %Y"))) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(umap_x, umap_y, color = Subreddit), size = 1.5) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "UMAP Projections of 50-Dimensional Doc2Vec Results",
         subtitle = paste("Prompt: \"", prompts$Prompt[5], "...\"", sep = "")) +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_grid(Subreddit ~ Quarter)

  ggsave("plots/umap/h1-2018.jpg",
         plot = plot,
         height = 6,
         width = 6)  
```

T test to assess significance of above results
```{r}
t_test_data <- data_umap %>%
    filter(Prompt == as.character(prompts$Prompt[5]),
           Quarter == "Q1 2018" | Quarter == "Q2 2018") %>%
  select(label, umap_x, umap_y, Quarter)

#Dem T Test - two periods
dem_t_q1 <- t_test_data %>%
  filter(label == "democrats",
         Quarter == "Q1 2018") %>%
  select(umap_x) %>%
  pull()

dem_t_q2 <- t_test_data %>%
  filter(label == "democrats",
         Quarter == "Q2 2018") %>%
  select(umap_x) %>%
  pull()

t.test(dem_t_q1, dem_t_q2)

demy_t_q1 <- t_test_data %>%
  filter(label == "democrats",
         Quarter == "Q1 2018") %>%
  select(umap_y) %>%
  pull()

demy_t_q2 <- t_test_data %>%
  filter(label == "democrats",
         Quarter == "Q2 2018") %>%
  select(umap_y) %>%
  pull()

t.test(demy_t_q1, demy_t_q2)

# Conservative t test

t_q1 <- t_test_data %>%
  filter(label == "conservative",
         Quarter == "Q1 2018") %>%
  select(umap_x) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(label == "conservative",
         Quarter == "Q2 2018") %>%
  select(umap_x) %>%
  pull()

t.test(t_q1, t_q2)

t_q1 <- t_test_data %>%
  filter(label == "conservative",
         Quarter == "Q1 2018") %>%
  select(umap_y) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(label == "conservative",
         Quarter == "Q2 2018") %>%
  select(umap_y) %>%
  pull()

t.test(t_q1, t_q2)

# Socialism t test

t_q1 <- t_test_data %>%
  filter(label == "socialism",
         Quarter == "Q1 2018") %>%
  select(umap_x) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(label == "socialism",
         Quarter == "Q2 2018") %>%
  select(umap_x) %>%
  pull()

t.test(t_q1, t_q2)

t_q1 <- t_test_data %>%
  filter(label == "socialism",
         Quarter == "Q1 2018") %>%
  select(umap_y) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(label == "socialism",
         Quarter == "Q2 2018") %>%
  select(umap_y) %>%
  pull()

t.test(t_q1, t_q2)

# All t test

t_q1 <- t_test_data %>%
  filter(Quarter == "Q1 2018") %>%
  select(umap_x) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(Quarter == "Q2 2018") %>%
  select(umap_x) %>%
  pull()

t.test(t_q1, t_q2)

t_q1 <- t_test_data %>%
  filter(Quarter == "Q1 2018") %>%
  select(umap_y) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(Quarter == "Q2 2018") %>%
  select(umap_y) %>%
  pull()

t.test(t_q1, t_q2)

```



KS test to assess significance of above results
```{r}
t_test_data <- data_umap %>%
    filter(Prompt == as.character(prompts$Prompt[5]),
           Quarter == "Q1 2018" | Quarter == "Q2 2018") %>%
  select(label, umap_x, umap_y, Quarter)

#Dem T Test - two periods
dem_t_q1 <- t_test_data %>%
  filter(label == "democrats",
         Quarter == "Q1 2018") %>%
  select(umap_x) %>%
  pull()

dem_t_q2 <- t_test_data %>%
  filter(label == "democrats",
         Quarter == "Q2 2018") %>%
  select(umap_x) %>%
  pull()

ks.test(dem_t_q1, dem_t_q2)

demy_t_q1 <- t_test_data %>%
  filter(label == "democrats",
         Quarter == "Q1 2018") %>%
  select(umap_y) %>%
  pull()

demy_t_q2 <- t_test_data %>%
  filter(label == "democrats",
         Quarter == "Q2 2018") %>%
  select(umap_y) %>%
  pull()

ks.test(demy_t_q1, demy_t_q2)

# Conservative t test

t_q1 <- t_test_data %>%
  filter(label == "conservative",
         Quarter == "Q1 2018") %>%
  select(umap_x) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(label == "conservative",
         Quarter == "Q2 2018") %>%
  select(umap_x) %>%
  pull()

ks.test(t_q1, t_q2)

t_q1 <- t_test_data %>%
  filter(label == "conservative",
         Quarter == "Q1 2018") %>%
  select(umap_y) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(label == "conservative",
         Quarter == "Q2 2018") %>%
  select(umap_y) %>%
  pull()

ks.test(t_q1, t_q2)

# Socialism t test

t_q1 <- t_test_data %>%
  filter(label == "socialism",
         Quarter == "Q1 2018") %>%
  select(umap_x) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(label == "socialism",
         Quarter == "Q2 2018") %>%
  select(umap_x) %>%
  pull()

ks.test(t_q1, t_q2)

t_q1 <- t_test_data %>%
  filter(label == "socialism",
         Quarter == "Q1 2018") %>%
  select(umap_y) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(label == "socialism",
         Quarter == "Q2 2018") %>%
  select(umap_y) %>%
  pull()

ks.test(t_q1, t_q2)

# All t test

t_q1 <- t_test_data %>%
  filter(Quarter == "Q1 2018") %>%
  select(umap_x) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(Quarter == "Q2 2018") %>%
  select(umap_x) %>%
  pull()

ks.test(t_q1, t_q2)

t_q1 <- t_test_data %>%
  filter(Quarter == "Q1 2018") %>%
  select(umap_y) %>%
  pull()

t_q2 <- t_test_data %>%
  filter(Quarter == "Q2 2018") %>%
  select(umap_y) %>%
  pull()

ks.test(t_q1, t_q2)

```




```{r}
t_table <- data.frame(Subreddit = character(), 
                      Axis = character(),
                      t = numeric(),
                      p = numeric())

produce_t_table <- function(subreddit, axis){
  q1 <- t_test_data %>%
  filter(label == subreddit,
         Quarter == "Q1 2018") %>%
  select(axis) %>%
  pull()
  
  q2 <- t_test_data %>%
  filter(label == subreddit,
         Quarter == "Q2 2018") %>%
  select(axis) %>%
  pull()

t_results <- t.test(q1, q2)
  
t <- t_results$statistic[[1]]

p <- t_results$p.value
  
t_table %>%
  add_row(Subreddit = subreddit,
          Axis = axis,
          t = t,
          p = p)
}
```
Map Function to get results
```{r}
subreddits <- c("democrats", "conservative", "socialism")
axes <- c("umap_x", "umap_y")

cross2(subreddits, axes)
map2(subreddits, axes, produce_t_table)
```



```{r}
data_umap %>%
    filter(Prompt == as.character(prompts$Prompt[9]),
           Quarter == "Q1 2018" | Quarter == "Q2 2018") %>%
    mutate(Subreddit = label) %>%
  #  mutate(Quarter = as.Date(as.yearqtr(Quarter, "Q%q %Y"))) %>%
    distinct() %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(umap_x, umap_y, color = Subreddit), size = 1.5) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "UMAP Projections of 50-Dimensional Doc2Vec Results",
         subtitle = paste("Prompt: \"", prompts$Prompt[9], "...\"", sep = "")) +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_grid(Subreddit ~ Quarter)
```




### Scatter Plot of Monthly Averages - wrap label
```{r}
create_plot_monthly_average <- function(prompt){
  plot <- data %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    group_by(Date, Subreddit) %>%
    summarize(x_avg = mean(D2V_x),
              y_avg = mean(D2V_y)) %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(x_avg, y_avg, color = Date)) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Subreddit)
  
  ggsave(paste("plots/all-subreddits/monthly-average-subreddit/", prompt, ".jpg", sep = ""), plot = plot)
}
```

```{r}
map(prompts$Prompt, create_plot_monthly_average)
```



```{r}
data %>%
    filter(Prompt == as.character(prompts$Prompt[2])) %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    group_by(Date, Subreddit) %>%
    summarize(x_avg = mean(D2V_x),
              y_avg = mean(D2V_y)) %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(x_avg, y_avg, shape = Subreddit, color = Date), size = 3) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompts$Prompt[2], "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman')
```

```{r}
create_plot_monthly_average_date <- function(prompt){
  plot <- data %>%
    filter(Prompt == as.character(prompt)) %>%
    mutate(Date = date,
           Subreddit = label) %>%
    distinct() %>%
    group_by(Date, Subreddit) %>%
    summarize(x_avg = mean(D2V_x),
              y_avg = mean(D2V_y)) %>%
    #group_by(Prompt) %>%
    ggplot() +
    geom_point(aes(x_avg, y_avg, color = Subreddit)) +
    labs(x = "X Embedding",
         y = "Y Embedding",
         title = "2-Dimensional Doc2Vec Embeddings of Text Generation Results",
         subtitle = paste("Prompt: \"", prompt, "...\"", sep = ""),
         caption = "Trained on monthly corpora from r/Conservative, r/democrats, and r/socialism") +
    theme_bw(base_size=12, base_family='Times New Roman') +
    facet_wrap(~ Date)
  
  plot
   # ggsave(paste("plots/average-scatter/", prompt, ".jpg", sep = ""), plot = plot)
}
```

```{r}
map(prompts$Prompt, create_plot_monthly_average_date)
```

## Statistical Tests

### Is time significant?

Load data
```{r}
data <- read_csv("data/embeddings-2d-d2v.csv")
```


Create date column
```{r}
data <- data %>%
  select(Month, Year, Prompt, D2V_x, D2V_y) %>%
  mutate(Month = paste(0, Month, sep = "")) %>%
  mutate(date = paste(Month, Year, sep = "-")) %>%
  mutate(date = as.Date(as.yearmon(date, "%m-%Y")))
```


```{r}
month_ids <- data %>%
  select(date) %>%
  distinct() %>%
  mutate(id = row_number())

data_month_id <- data %>%
  left_join(month_ids)
```



```{r}
prompts <- data %>%
  select(Prompt) %>%
  distinct() %>%
  as.list()
```


Function to Test Time significance
```{r}

time_test <- function(prompt) {
df <- data_month_id %>%
  filter(Prompt == as.character(prompt)) %>%
  mutate(Date = date) %>%
  distinct()

#LM
x_results <- lm(D2V_x ~ id, df)
y_results <- lm(D2V_y ~ id, df)

#LM with polynomial term
x_results_poly <- lm(D2V_x ~ poly(id, 2), df)
y_results_poly <- lm(D2V_y ~ poly(id, 2), df)

#Results of LM
x_sum <- summary(x_results)
y_sum <- summary(y_results)

coef_x <- x_sum$coefficients[2, 1]
st_error_x <- x_sum$coefficients[2, 2]
p_value_x <- x_sum$coefficients[2, 4]

coef_y <- y_sum$coefficients[2, 1]
st_error_y <- y_sum$coefficients[2, 2]
p_value_y <- y_sum$coefficients[2, 4]

#Results of LM poly
#x
x_poly_sum <- summary(x_results_poly)
y_poly_sum <- summary(y_results_poly)

coef_x_1 <- x_poly_sum$coefficients[2, 1]
st_error_x_1 <- x_poly_sum$coefficients[2, 2]
p_value_x_1 <- x_poly_sum$coefficients[2, 4]

coef_x_2 <- x_poly_sum$coefficients[3, 1]
st_error_x_2 <- x_poly_sum$coefficients[3, 2]
p_value_x_2 <- x_poly_sum$coefficients[3, 4]

#y
coef_y_1 <- y_poly_sum$coefficients[2, 1]
st_error_y_1 <- y_poly_sum$coefficients[2, 2]
p_value_y_1 <- y_poly_sum$coefficients[2, 4]

coef_y_2 <- y_poly_sum$coefficients[3, 1]
st_error_y_2 <- y_poly_sum$coefficients[3, 2]
p_value_y_2 <- y_poly_sum$coefficients[3, 4]

#Collect all results into table
x_results <- c(coef_x, st_error_x, p_value_x, NA, NA, NA)
y_results <- c(coef_y, st_error_y, p_value_y, NA, NA, NA)

x_poly_results <- c(coef_x_1, st_error_x_1, p_value_x_1, coef_x_2, st_error_x_2, p_value_x_2)
y_poly_results <- c(coef_y_1, st_error_y_1, p_value_y_1, coef_y_2, st_error_y_2, p_value_y_2)

results <- rbind(x_results, y_results, x_poly_results, y_poly_results)

colnames(results) <- c("Coefficient", "St. Dev", "P Value", "Poly Coefficient", "Poly St. Dev", "Poly P Value")

output <- list(prompt, results)

return(output)

}
```


```{r}
regression_results <- map(prompts$Prompt, time_test)
regression_results
```

Collect regression results into single table
```{r}
prompt <- regression_results[1][[1]][[1]][1]
reg_table <- data.frame(regression_results[1][[1]][[2]]) %>%
  rownames_to_column() %>%
  mutate(prompt = as.character(prompt)) %>%
  select(prompt, rowname:Poly.P.Value)

regtable
  
```

Function for reg results
```{r}
collect_reg_results <- function(prompt_id) {
  prompt <- regression_results[prompt_id][[1]][[1]][1]
  
  reg_table <- data.frame(regression_results[prompt_id][[1]][[2]]) %>%
  rownames_to_column() %>%
  mutate(prompt = as.character(prompt)) %>%
  select(prompt, rowname:Poly.P.Value)

  reg_table
}
```


```{r}
all_reg_results <- map_dfr(seq(1:8), collect_reg_results)

write_csv(all_reg_results, "data/all_reg_results.csv")
```


